
\section{Game rules}

\medskip In this game, four players have control over an army of
farmers, knights and witches on a $37 \times 37$ board.

\medskip The goal of the game is to ``farm'' as many cells as possible,
converting them to the team color. Initially, the cells have no color.
Every round, the number of cells of each color is added to the
corresponding score. The winner of the game is the player with the
highest score after the last round.

\medskip Each player has a quadrant where their units are initially
born, and where they are reborn when captured (killed) from other
teams. Player 0 has the top-left quadrant, player 1 the bottom-left
quadrant, player 2 the bottom-right \mbox{quadrant}, and player 3 the
top-right quadrant. At the beginning of the game, each player gets 20
farmers, 10 knights and 2 witches on its quadrant.

\medskip The game lasts 200 rounds. Every round, every player can move
each own unit at most once. Farmers  and witches can only move
horizontally and vertically. Knights can also move diagonally, and
attack rival units.

\medskip The boards have walls, that is, obstacles that units cannot
visit nor traverse. The top row, bottom row, lef-most column, and
right-most column only have walls. Trying to move a unit into a wall is
an invalid move.

\medskip Initially, farmers have health 100, and knights have health
200. Deliberately not moving a unit (or moving it in the \texttt{None}
direction) will increase its health by 30~units. A unit cannot have
more health than its initial amount. Performing an invalid move results
in that unit not moving, but does not regenerate health.

\medskip Witches are immortal. Witches can move to any adjacent empty
cell. Any cell at Manhattan distance at most two from a witch (that is,
at most two horizontal or vertical steps away from a witch, or
diagonally adjacent to a witch) is haunted, even if there is a wall in between.
Any farmer or knight in a
haunted cell dies immediately, even if the spell comes from a witch of
the own team.

\medskip A witch gets ``deactivated'' when there are one or more
witches at Manhattan distance at most two from her, even if there is
just one such witch, and from the same team. Deactivated witches do not
haunt any sorrounding cells, and farmers and knights can move around
them (until the witches get activated again, of course).

\medskip Farmers can move to any adjacent empty cell. If that cell is
haunted, the farmer dies. Otherwise, the cell is painted with the
farmer's team color.

\medskip Knights can move to any adjacent or diagonally adjacent empty
cell. If that cell is haunted, the knight dies.

\medskip A unit killed by the spell of one or more witches
will be reborn as a unit of another team.
If all the killing witches belong to the same team of the dead unit,
the new team will be selected uniformly at random among the rest of teams.
Otherwise, the new team will be selected with probability proportional
to the number of killing witches of the other teams.
For instance, if a unit of player 2 dies under the spell
of one witch of team 0, two witches of team 1,
and one witch of team 2,
then the new team will be 0 with probability $1/3$,
and will be 1 with probability $2/3$.

\medskip Knights can attack any adjacent or diagonally adjacent
rival farmer or rival knight (by an order to move there).
Trying to attack an own unit or a witch
is an invalid movement. Otherwise, the rival unit loses a random amount
of health between 60 and 90. If the new health drops to 0 or below,
that unit is captured by the team of the attacking knight.

\medskip Every round, more than one order can be given to the same
unit, although only the first such order (if any) will be selected. Any
player program that tries to give more than 1000 orders during the same
round will be aborted.

\medskip Every round, all the selected orders will be executed using a
random order. For instance, if two farmers try to move to the same
empty cell, only the farmer that happens to move first will move there.
As another example, assume that one farmer and one rival knight
try to move to the same empty cell.
If the knight happens to move first,
afterwards the farmer will not move,
because it would be an illegal movement.
However, if the farmer moves first,
afterwards the knight will attack the farmer,
by trying to move to the farmer's position.

\medskip After all the selected movements of a round are played, the
units captured by each team are reborn in its corresponding quadrant.
Whenever possible, all units are reborn at Manhattan distance at least
3 from witches. Additionally, farmers are not placed adjacent to rival
knights, and knights are not placed adjacent or diagonally adjacent to
any rival unit. In the rare cases when this cannot be accomplished,
units are reborn on any legal cell in the own quadrant, or on any legal
cell in any other quadrant, in even more exceptional situations.

\medskip Although there are four players, with numbers 0 to 3, when
programming your strategy you must always assume that you are player 0.
If you are not, the board will be rotated consistently with your
illusion. For instance, if you are player 1, any movement in the
\texttt{Right} direction by you will be automatically transformed into
a movement to the \texttt{Top}.

\medskip Note that the valid directions are
\texttt{Bottom}, \texttt{BR}, \texttt{Right}, \texttt{RT}, \texttt{Top},
\texttt{TL}, \texttt{Left}, \texttt{LB} and \texttt{None},
corresponding to integers from 0 to 8.
This circular definition can be used
to simplify the implementation of your player.
See the \texttt{Demo} player for some examples.

\medskip If you need (pseudo) random numbers,
you must use two methods provided by the game:
\texttt{random(l, u)}, which returns a random integer in \texttt{[l..u]},
and (less frequently) \texttt{random\_permutation(n)},
which returns a \texttt{vector<int>}
with a random permutation of \texttt{[0..n-1]}.

\medskip A game is defined by a board and the following set of parameters:

\begin{itemize}
  \item @nb_players@: Number of teams in the game (4).
  \item @nb_rounds@: Number of rounds that will be played (200).
  \item @nb_farmers@: Initial number of farmers per player (20).
  \item @nb_knights@: Initial number of knights per player (10).
  \item @nb_witches@: Constant number of witches per player (2).
  \item @farmers_health@: The maximum (and initial) health of a farmer (100).
  \item @knights_health@: The maximum (and initial) health of a knight (200).
  \item @farmers_regen@: The amount of health a farmer will regenerate when not moving (30).
  \item @knights_regen@: The amount of health a knight will regenerate when not moving (30).
  \item @damage_min@: The minimum amount of damage a knight will inflict when attacking (60).
  \item @damage_max@: The maximum amount of damage a knight will inflict when attacking (90).
  \item @rows@: Vertical size of the board (37).
  \item @cols@: Horizontal size of the board (37).
\end{itemize}

